---
title: "Introduction to the fars Package"
author: "Your Name"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the fars Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(fars)
```

## Overview

The fars package provides tools for reading, summarizing, and visualizing data from the Fatality Analysis Reporting System (FARS). This vignette introduces the main functions with simple examples.

## Reading Data

Use fars_read() to read a FARS CSV file.
```{r}
filename <- system.file("extdata", "accident_2013.csv.bz2", package = "fars")
head(fars_read(filename))

```
## Summarizing Data by Year

You can summarize accidents per month across one or more years:
```{r}
fars_summarize_years(c(2013, 2014))

```

## Plotting Accidents on a Map

You can visualize accident locations for a specific state and year using fars_map_state():
```{r}
fars_map_state(1, 2013)  # Plots accidents in state 1 for 2013

```

## Error Handling

The functions are designed to handle common errors gracefully, such as invalid filenames or state numbers. For example:
```{r}
fars_map_state(1000, 2013)  # Triggers error for invalid state

```

## Accessing Example Data

Example data files can be accessed using:
```{r}
system.file("extdata", "accident_2013.csv.bz2", package = "fars")

```

This vignette gives a basic tour. See the documentation of individual functions for more.

